Using CopyKAT to idenfity tumor cells in Ewing sarcoma samples

### 2024-05-28 analyses/cell-type-ewings/template_notebooks/03-copykat.Rmd
fix spelling in notebook
simplify template notebook defaults

---
title: "Using CopyKAT to idenfity tumor cells in Ewing sarcoma samples"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "../results/annotate_tumor_cells_output/SCPCS000490/SCPCL000822_tumor-normal-classifications.tsv"
  no_ref_copykat_results: "../results/annotate_tumor_cells_output/SCPCS000490/copykat/no_reference"
  with_ref_copykat_results: "../results/annotate_tumor_cells_output/SCPCS000490/copykat/with_reference"
  reference_cell_file: "../results/annotate_tumor_cells_output/SCPCS000490/annotations/SCPCL000822_reference-cells.tsv"
  results_dir: "../results/annotate_tumor_cells_output/SCPCS000490"
---

@@

obj_file <- glue::glue("{params$library_id}_final-copykat.rds")
png_file <- glue::glue("{params$libary_id}_copykat_heatmap.jpeg")

>>>>

---
title: "Using CopyKAT to idenfity tumor cells in Ewing sarcoma samples"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  no_ref_copykat_results: "copykat/no_reference"
  with_ref_copykat_results: "copykat/with_reference"
  reference_cell_file: ".reference-cells.tsv"
  results_dir: "annotate_tumor_cells_output"
---

@@

obj_file <- glue::glue("{params$library_id}_final-copykat.rds")
png_file <- glue::glue("{params$library_id}_copykat_heatmap.jpeg")
